Presentation Title

### 2017-06-15 thesis/chapters/ch4-implementation.tex
Better figures

@@

\section{Evaluation}
\begin{itemize}
  \item How fast is the consensus algorithm? Possibly plot graph of time versus
    the number of nodes.
  \item Does the promoter registration phase add a lot of extra overhead?
  \item What's the rate of transaction such that they can be verified ``on
    time'', i.e. without a growing backlog?
  \item Our global validation rate is somewhat equivalent to the transaction
    rate in other systems. Does the validation rate scale with respect to the
    number of nodes? In theory it should. Plot validation rate vs number of
    nodes, we expect it to be almost linear.
\end{itemize}

>>>>

\begin{figure}[h]
  \centering
  \begin{subfigure}{\textwidth}
    \includegraphics[width=\textwidth]{result-normal-cons-vs-facilitator}
  \end{subfigure}

  \begin{subfigure}{\textwidth}
    \includegraphics[width=\textwidth]{result-rand-cons-vs-facilitator}
  \end{subfigure}
\end{figure}

\begin{figure}[h]
  \centering
  \begin{subfigure}{\textwidth}
    \includegraphics[width=\textwidth]{result-normal-cons-vs-pop}
  \end{subfigure}

  \begin{subfigure}{\textwidth}
    \includegraphics[width=\textwidth]{result-rand-cons-vs-pop}
  \end{subfigure}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \begin{subfigure}{\textwidth}
    \includegraphics[width=\textwidth]{result-normal-throughput-vs-pop}
  \end{subfigure}

  \begin{subfigure}{\textwidth}
    \includegraphics[width=\textwidth]{result-rand-throughput-vs-pop}
  \end{subfigure}
\end{figure}
\section{Evaluation}
\begin{itemize}
  \item How fast is the consensus algorithm? Possibly plot graph of time versus
    the number of nodes.
  \item Does the promoter registration phase add a lot of extra overhead?
  \item What's the rate of transaction such that they can be verified ``on
    time'', i.e. without a growing backlog?
  \item Our global validation rate is somewhat equivalent to the transaction
    rate in other systems. Does the validation rate scale with respect to the
    number of nodes? In theory it should. Plot validation rate vs number of
    nodes, we expect it to be almost linear.
\end{itemize}
